FinalManuscript_DISCS_UG

### 2019-02-18 pcsc-paper/parts/03_exponentialandlogarithmic.tex
Remove timing results, tweaked graphs

\begin{figure}[ht]
	\centering
    \begin{tikzpicture}
		\begin{semilogyaxis}[
			% height=6cm, width=9cm,
			xmin=0, xmax=300,
			ymin=1e-10, ymax=1.4,
			xlabel={$x$}, ylabel={Absolute error},
			grid=major,
			legend pos=south east,
			legend cell align=left,
			tick scale binop=\times,
		]
		% \addplot[very thick, domain=0:300, samples=500]{abs(-1/30*(x^5*(30*ln(1/16) - 137) + 45*x^4*(270*ln(1/16) - 593) + 30*x^3*(27210*ln(1/16) - 20579) + 30*x^2*(488810*ln(1/16) + 216621) + 45*x*(1690670*ln(1/16) + 2694207) + 93677310*ln(1/16) + 257804775)/(x^5 + 405*x^4 + 27210*x^3 + 488810*x^2 + 2536005*x + 3122577) - ln(x + 1))};
		% \addplot[very thick, domain=0:300, samples=300]{abs(1/30*(137*x^5 + 26685*x^4 + 617370*x^3 - 6498630*x^2 - 121239315*x - 257804775)/(x^5 + 405*x^4 + 27210*x^3 + 488810*x^2 + 2536005*x + 3122577) - ln(1/16) - ln(x + 1))};
		\addplot[very thick, ACMDarkBlue] table[x=x, y=error] {plots/abs_err_scaledlog.txt};
		\addplot[densely dashed, domain=0:300, samples=100]{abs(1/30*(137*x^5 + 2310*x^4 + 9870*x^3 + 15120*x^2 + 7560*x)/(x^5 + 30*x^4 + 210*x^3 + 560*x^2 + 630*x + 252) - ln(x + 1))};
		\legend{Scaled quadrature ($\alpha = 1/16$), Original quadrature ($\alpha = 1$)}
	\end{semilogyaxis}
	\end{tikzpicture}%
	\caption{Comparison of the absolute error between the original approximation in Equation~\ref{eq:standard_logarithm_quadrature} and the scaled approximation in Equation~\ref{eq:optimal_log_approximation}}
	\label{fig:log_error_comparison}
\end{figure}

>>>>

\begin{figure}[ht]
	\centering
    \begin{tikzpicture}
		\begin{semilogyaxis}[
			% height=6cm, width=9cm,
			xmin=0, xmax=300,
			ymin=1e-10, ymax=1.4,
			xlabel={$x$}, ylabel={Absolute error},
			grid=major,
			legend pos=south east,
			legend cell align=left,
			tick scale binop=\times,
		]
		% \addplot[very thick, domain=0:300, samples=500]{abs(-1/30*(x^5*(30*ln(1/16) - 137) + 45*x^4*(270*ln(1/16) - 593) + 30*x^3*(27210*ln(1/16) - 20579) + 30*x^2*(488810*ln(1/16) + 216621) + 45*x*(1690670*ln(1/16) + 2694207) + 93677310*ln(1/16) + 257804775)/(x^5 + 405*x^4 + 27210*x^3 + 488810*x^2 + 2536005*x + 3122577) - ln(x + 1))};
		% \addplot[very thick, domain=0:300, samples=300]{abs(1/30*(137*x^5 + 26685*x^4 + 617370*x^3 - 6498630*x^2 - 121239315*x - 257804775)/(x^5 + 405*x^4 + 27210*x^3 + 488810*x^2 + 2536005*x + 3122577) - ln(1/16) - ln(x + 1))};
		\addplot[thick, ACMOrange, domain=0:300, samples=100]{abs(1/30*(137*x^5 + 2310*x^4 + 9870*x^3 + 15120*x^2 + 7560*x)/(x^5 + 30*x^4 + 210*x^3 + 560*x^2 + 630*x + 252) - ln(x + 1))};
		\addplot[very thick, ACMDarkBlue] table[x=x, y=error] {plots/abs_err_scaledlog.txt};
		\legend{Original quadrature ($\alpha = 1$), Scaled quadrature ($\alpha = 1/16$)}
	\end{semilogyaxis}
	\end{tikzpicture}%
	\caption{Comparison of the absolute error between the original approximation in Equation~\ref{eq:standard_logarithm_quadrature} and the scaled approximation in Equation~\ref{eq:optimal_log_approximation}}
	\label{fig:log_error_comparison}
\end{figure}
